\documentclass[a4paper, twocolumn]{article}

\usepackage[a4paper, left=14.5mm, right=15mm, top=20mm, bottom=32mm]{geometry}
\usepackage[english]{babel}

\pagenumbering{arabic}
\bibliographystyle{}

\title{
	\LARGE{
		\textbf{
			Project Heirs Briefing
		}
	}
}

\author{
	Farhad Modaresi\footnote{Bachelors student of electrical engineering}
}

\begin{document}
\maketitle


\begin{abstract}
	This project aims to provide a full line-up of bench power supplies, packed with novel features and low price tags, to fill the hollow points in rather disturbed Iranian market. There has been extreme instability in Iranian Rial's value and as a result bench power supplies, widely used in different industries, have experienced price multiplications of up to 10x. In general it is a tragic incident, but it also opens up new opportunities that we could use to our benefit. We would be able to provide a competitive price tag in low-end products and by implementing novel ideas and thus securing a high market share. 
\end{abstract}
\section*{Introduction}
A power supply is an electrical device that supplies electric power from a source to the load with desired voltage, current, and frequency. A bench power supply is a standard piece of test and measurement equipment on every electrical engineer and circuit designer’s bench.  
\section*{The Problem}
Well it is fair to say that in Iran 
\section*{The Solution}
\section*{Price Considerations}
\section*{Competition}
\section*{Conclusion}


\begin{enumerate}
 \item A 100 word or less summary indicating on scientific grounds
why the paper should be considered for a wide-ranging journal like
\textsl{Nature} instead of a more narrowly focused journal.
 \item A 100 word or less summary aimed at a non-scientific audience,
written at the level of a national newspaper.  It may be used for
\textsl{Nature}'s press release or other general publicity.
 \item The cover letter should state clearly what is included as the
submission, including number of figures, supporting manuscripts
and any Supplementary Information (specifying number of items and
format).
 \item The cover letter should also state the number of
words of text in the paper; the number of figures and parts of
figures (for example, 4 figures, comprising 16 separate panels in
total); a rough estimate of the desired final size of figures in
terms of number of pages; and a full current postal address,
telephone and fax numbers, and current e-mail address.
\end{enumerate}

\end{document}
